---
title: "dav"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dav}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dav)
```

Data asset valuation is an emerging cross-discipline area of research that seeks
to manage data as if they were intangible assets.

## Methodology
The value of a data asset is equal to the sum of the value of its smallest 
meaningful attributes. For data these are collections of bits and the semantics
that the beholder perceives.

## Data value attributes
<!--- insert list and description of DVA here --->

## Limitations

Ascribing an exact value to a set of data is currently impossible. Indeed, a 
unified definition of what exactly are data, information and what their value 
attributes are, is a disputed topic. To arrive at an informative approximation
assumptions must be made.

- the asset supplied contains (mostly) *truthful* relata
- domain expert opinions are meaningful for the attributes to be valued